Sequential algorithms to split and merge terabyte-scale 3D images

### 2017-07-04 paper.tex
Fixed number of seeks for multiple reads
change mreads algo pseudocode

@@

\begin{algorithm}[h]
  \caption{Buffered merging from blocks using multiple reads
    \todo{improve notations and algo}.}
  \label{algo:multiple-reads}
  \begin{algorithmic}
    \STATE list = sort blocks by increasing (x,y,z) values
    \STATE initialize buffer
    \STATE pointer = 0, max\_index=(m-1)
    \WHILE{max\_index \textless sizeof(reconstructed\_image)}
    \WHILE{pointer \textless max\_index}
        \STATE block = read block that contains voxel index\_to\_voxel(pointer)
        \STATE insert in buffer all voxels (x,y,z) of block where voxel\_to\_index(x,y,z) \textless max\_index
        \STATE update pointer to point to the next unassigned element in buffer
        \ENDWHILE
       \STATE write buffer in reconstructed image
       \STATE clear buffer
       \STATE pointer = max\_index + 1
       \STATE max\_index += m
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

\begin{equation}
  N_\mathrm{multiple\_reads}= n \max\left(1,\ceil*{\frac{d}{\ceil*{\frac{m}{nd^2b}}}}\right)+ \ceil*{\frac{bR}{m}}
\end{equation}

@@

>>>>

%\href{http://dl.acm.org/citation.cfm?id=218395}

\newpage

@@

\begin{algorithm}[h]
  \caption{Buffered merging from blocks using multiple reads
    \todo{improve notations and algo}.}
  \label{algo:multiple-reads}
  \begin{algorithmic}
  \STATE sorted\_split\_name\_list = sort blocks by increasing (x,y,z) values 
  \STATE start\_index = 0, end\_index=(m-1)
  \WHILE{end\_index \textless sizeof(reconstructed\_image)}
    \STATE initialize data\_buffer
    \FOR{split\_name in sorted\_split\_name\_list}
      \IF{indexes of split\_name is in next\_write\_range}
        \STATE read split;
        \STATE extract all indexes in next write range;
        \STATE assgin the corresponding data to the data\_buffer
      \ENDIF
    \ENDFOR
    \STATE write data\_buffer in reconstructed\_image 
    \STATE clear data\_buffer
    \STATE start\_index = end\_index + 1
    \STATE end\_index += mem
  \ENDWHILE

  \end{algorithmic}
\end{algorithm}

\begin{equation}
  N_\mathrm{multiple\_reads}= n\left( \ceil*{\frac{\left((d-1)D^2+dD\right)b}{m}}\right) + 2\ceil*{\frac{bR}{m}}
\end{equation}

@@

\newpage
